---
title: "Week1"
output: html_document
date: "2025-09-24"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown


1: Create a data frame

```{r}
animals <- c("Snake", "Ostrich", "Cat", "Spider")
animals

num_legs <- c(0,2,4,8)
num_legs

animal_df <- data.frame(animals, num_legs)
print(animal_df)
```
2: Create a data frame
```{r}
ls()
```
## Including Plots

3: Create a data frame in R Scripts
```{r}
# see in myFirstRScript
```

4: Create a data frame in R Markdown
```{r}
# It is this file
```

5: Matrix operations
```{r}
x_vect <- seq(12, 2, by = -2)
x_vect

X <- matrix(x_vect, 2,3)
X

Y <- matrix(seq(1,4), 2, 2)
Y

Z <- matrix(seq(4, 10, by = 2), 2, 2)
Z

#the transpose of these matrix
Yt <- t(Y)
Yt

Zt <- t(Z)
Zt

#Matricx sums
Y + Z

#Matrix multiplication
Y * Z #element-wise matrix multiplication

#the proper matrix products AB
Y %*% Z

Y %*% X

#Matrix inverse
solve(Y)
Y %*% solve(Y)

solve(Y, X)
```
6: Writing a function within R
```{r}
myFirstRFunc <- function(n){
  stopifnot(is.numeric(n), n > 0)
  
  temp <- seq(1, n-1)
  sum <- 0
  for(i in temp){
    if(i %% 2 == 0|i %% 7 == 0){
      #print(i)
      sum <- sum + i
    }
  }
  return(sum)
}

myFirstRFunc(1000)
```
7: Futher R Markdown exercises
Wave plot
```{r}
x <- seq(0,20,0.01,)

y <- sin(x)

sin_df <- data.frame(x,y)
#head(sin_df,3)
#sin_df

plot(sin_df)
```

You can also embed plots, for example:

```{r, echo = FALSE}

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
